---
title: "Project Documentation"
author: "apb766, jdg3666, mew2795"
date: "September 30, 2015"
output: html_document
---
1. The first step of this project was to take the .csv file "hygdata_v3.csv" and reformat it using ETL code, which can be found in the 01 Data folder. This produced SQL code to create a table in Oracle and a reformatted csv file which was fit to be uploaded to oracle.

```{r}
source("../01 Data/ETL_code.R", echo = TRUE)
```

2. This chunk of R calls a program which queries the oracle database for the table "StarData10k" and displays a summary and subset of the data. You can see that that data has a lot of columns, so our workflows are crucial to narrowing down the amount of data.

```{r}
source("../01 Data/Database Creation Code.R", echo = TRUE)
```
3. The first workflow takes the dataframe (df) and selects 5 columns (ID, DIST, CON, ABSMAG, MAG), filters out stars where the Constellation is Null, and arranges it by Constellation and distance from Earth. 

The first visualization shows the star's magnitude (its brightness as seen from Earth) compared to which constallation it's in.
```{r}
source("../02 Data Wrangling/Workflow 1.R", echo = TRUE)
```

This Visualization shows that the constellations all have a relatively similar distribution of magnitudes around 8.5

In the second work flow, from the dataframe (df), ID, DIST, CON and LUM are selected, filtering out stars that are not in constellations and only taking the top 99% the most luminous stars.

The second visualization shows the top 99% of luminosity of stars across distance to the Earth, colored by constellations.
```{r}
source("../02 Data Wrangling/Workflow 2.R", echo = TRUE)
```

This graph shows that all of the most luminous stars are located relatively equidistant from the Earth. This is an interesting idea, showing that the variability in distance from the Earth is similar for the top 100 stars in the databse.

This visualization shows the stars that have a non-zero radial velocity colored by magnitude
As part of my investigation I used the group_by function in my workflow to generate a table that shows the number of stars that each constellation has in this dataset.

```{r}
source("../02 Data Wrangling/Workflow 4.R", echo = TRUE)
```

This graph shows that the majority of stars in this dataset have a relation between the radial velocity and the x velocity. If the x-velocity is negative the radial velocity will be negative and if the x-volocity is positive the radial velocity will be positive.
